03 Data Vizualization

### 2022-06-07 03_data_viz.Rmd
updated FA profile and det lim

  # Plot it
  ggplot(
    aes(
      x = u_d_mc,
      y = compound,
      color = type,
      fill = type
      )
  ) +
  geom_point(size = 2) +
  geom_errorbar(aes(
    xmin = u_d_mc - (0.5 * su_d_mc),
    xmax = u_d_mc + (0.5 * su_d_mc)),
    width = 0,
    size = 1.1
    ) +
  coord_cartesian(xlim = c(0, 0.175)) +
  scale_fill_manual(values = c("black", color_choice)) +
  scale_color_manual(values = c("black", color_choice)) +
  theme_classic() +
  labs(x = TeX("Turnover ($day^{-1}$)"),
       title = terrain_choice) +
  theme(
    axis.title.y = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.ticks.y = element_blank(),
    strip.background = element_blank(),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5),
  )

@@

# cowplot::save_plot(
#   filename = "fig_output/p_turnover.pdf",
#   plot = p_turnover,
#   base_width = 11,
#   base_height = 4
#   )

@@

```{r}
p_dl <- dl_df %>% 
  ggplot(
    aes(x = extraction_deriv_efficiency_frac*100,
        y = detection_limit_cells,
        fill = as.factor(extraction_deriv_efficiency_frac))) +
  geom_col() +
  scale_x_continuous(breaks = c(20, 30, 40, 50, 60, 70, 80, 90, 100)) +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) +
  coord_cartesian(xlim = c(10, 110), ylim = c(1e4, 1e10)) +
  scale_fill_grey(start = 0.4, end = 0.1) +
  annotation_logticks(sides = "l") +
  labs(
    x = "Combined extraction and derivatization efficiency (%)",
    y = TeX("$^2 H$ detection limit (cells)")
  ) +
  theme_bw() +
  theme(
    legend.position = "NA",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 8)
  )
p_dl

cowplot::save_plot(
  plot = p_dl,
  filename = "fig_output/detection_limit_cells.pdf",
  base_height = 4,
  base_width = 4
)

@@

## (FAILING) Fatty Acid Abundances

```{r}
turnover_summarized %>% 
  filter(compound != "H2") %>% 
  filter(compound != "i-16:0") %>% 
  mutate(compound_edit = str_remove(compound, "-")) %>% 
  mutate(C_num = parse_number(compound_edit)) %>% 
  mutate(C_num = as.numeric(C_num)) %>% 
  mutate(compound = forcats::fct_reorder(compound, C_num)) %>% 
  ggplot(aes(x = compound,
             y = area_FID,
             fill = terrain,
             color = terrain)) +
  geom_col() +
  facet_wrap(vars(terrain, inc_time_d),
             scales = "free_y") +
  scale_fill_manual(values = terrain_fill_swatch) +
  scale_color_manual(values = terrain_color_swatch) +
  theme_bw() +
  labs(x = "Analyte",
       y = TeX("Peak Area ($pA \\cdot s$)"),
       fill = "Terrain",
       color = "Terrain") +
  theme(
    axis.text.x = element_text(angle = 90)
  )
```

>>>>

  # Plot it
  ggplot(
    aes(
      x = u_d_mc,
      y = compound,
      color = type,
      fill = type
      )
  ) +
  geom_point(size = 2) +
  geom_errorbar(aes(
    xmin = u_d_mc - (0.5 * su_d_mc),
    xmax = u_d_mc + (0.5 * su_d_mc)),
    width = 0,
    size = 1.1
    ) +
  coord_cartesian(xlim = c(0, 0.175)) +
  scale_fill_manual(values = c("black", color_choice)) +
  scale_color_manual(values = c("black", color_choice)) +
  scale_x_discrete(labels =)
  theme_classic() +
  labs(x = TeX("Turnover ($day^{-1}$)"),
       title = terrain_choice) +
  theme(
    axis.title.y = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.ticks.y = element_blank(),
    strip.background = element_blank(),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5),
    panel.grid.major.x = element_line(linetype = "dotted")
  )

@@

cowplot::save_plot(
  filename = "fig_output/turnover_plot.pdf",
  plot = p_turnover,
  base_width = 11,
  base_height = 4
  )

@@

```{r}
p_dl <- dl_df %>% 
  ggplot(
    aes(x = extraction_deriv_efficiency_frac*100,
        y = detection_limit_cells,
        fill = as.factor(extraction_deriv_efficiency_frac))) +
  geom_col() +
  geom_hline(yintercept = 1e10,
             linetype = "dotted",
             color = "red") +
  geom_hline(yintercept = 1e9,
             linetype = "dotted",
             color = "blue") +
  scale_x_continuous(breaks = c(20, 30, 40, 50, 60, 70, 80, 90, 100)) +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
              labels = trans_format("log10", math_format(10^.x))) +
  coord_cartesian(xlim = c(10, 110), ylim = c(1e4, 1e10)) +
  scale_fill_grey(start = 0.4, end = 0.1) +
  annotation_logticks(sides = "l") +
  labs(
    x = "Combined extraction and derivatization efficiency (%)",
    y = TeX("$^2 H$ detection limit (cells)")
  ) +
  theme_bw() +
  theme(
    legend.position = "NA",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 8)
  )
p_dl

# cowplot::save_plot(
#   plot = p_dl,
#   filename = "fig_output/detection_limit_cells.pdf",
#   base_height = 4,
#   base_width = 4
# )

@@

## (PASSING) Fatty Acid Abundances

```{r}
turnover_summarized %>% 
  filter(compound != "H2") %>% 
  filter(compound != "i-16:0") %>% 
  filter(compound != "16:1:ω5c") %>% 
  mutate(compound_edit = str_remove(compound, "-")) %>% 
  mutate(C_num = parse_number(compound_edit)) %>% 
  mutate(C_num = as.numeric(C_num)) %>% 
  mutate(compound = forcats::fct_reorder(compound, C_num)) %>% 
  ggplot(aes(x = compound,
             y = area_FID,
             fill = terrain,
             color = terrain)) +
  geom_col() +
  facet_wrap(vars(terrain, inc_time_d),
             scales = "free_y") +
  scale_fill_manual(values = terrain_fill_swatch) +
  scale_color_manual(values = terrain_color_swatch) +
  theme_classic() +
  labs(x = "Analyte",
       y = TeX("Peak Area ($pA \\cdot s$)"),
       fill = "Terrain",
       color = "Terrain") +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.position = "NA"
  )
```
